\vspace*{1cm}
\begin{center}
	\textbf{GENERAL INFORMATION} \\
	\ \\[\baselineskip]

	\textcolor{\primarycolor}{\textbf{Host and Organisers}}	 \\
	Department of Psychology, University of Hamburg: \\
	PD Dr. Patrick Bruns, Prof. Dr. Sebastian Gluth, Prof. Dr. Anja Riesel, Prof. Dr. Brigitte Röder, Prof. Dr. Nico Schuck, Prof. Dr. Lars Schwabe, Prof. Dr. Jan Wacker \\
	\vspace*{0.1cm}
	Department of Systems Neuroscience, University Medical Center Hamburg-Eppendorf: \\
	Dr. Helen Blank \\
	\vspace*{0.1cm}
	Department of Psychology, University of Bielefeld: \\
	Prof. Dr. Tina Lonsdorf \\
	\ \\[\baselineskip]
	\vspace*{0.1cm}
	
	\textcolor{\primarycolor}{\textbf {Scientific Committee}}	 \\
	The Psychologie und Gehirn (PuG) 2024 conference is organised in close collaboration with the Fachgruppe Biologische Psychologie und Neuropsychologie (FGBPNP) of the German Psychological Association (DGPs) and the Deutsche Gesellschaft für Psychophysiologie und ihre Anwendung (DGPA). We thank the president of the DGPA, Prof. Peter Kirsch, for his support. Prof. Lonsdorf is both speaker of the FGBPNP and part of the organizing committee.
	\\[\baselineskip]
	\vspace*{0.1cm}

	\textcolor{\primarycolor}{\textbf {Contact}}	 \\
	\textbf{Website:} https://www.pug2024.de \\
	\textbf{E-Mail:} pug2024@uni-hamburg.de
	\\[\baselineskip]
	\vspace*{0.1cm}

	\textcolor{\primarycolor}{\textbf {Acknowledgementst}}	 \\
	We want to express our thanks to all sponsors for their financial support. We are grateful for the support of all postdocs, PhD students, student assistants, and secretaries in preparing and running this conference. Special thanks go to Celestina Hermida da Costa for designing and managing the website and to Max Harkotte for providing us with the code to create this booklet.

\end{center}
\mbox{}
\thispagestyle{empty}
\vfill
\begin{center}
	\ \\[20pt] % Please cite us by keeping the following line.
	The open-source \LaTeX{} template, AMCOS\_booklet, used to generate this booklet is available at \url{https://github.com/maximelucas/AMCOS\_booklet}
\end{center}

\newpage