Dear colleagues, or simply put: Moin!
 
It is with great pleasure that we welcome you to the 49th Annual Psychologie und Gehirn (PuG) Conference, which will be held at the Universität Hamburg and the Bürgerhaus Wilhelmsburg from May 29 to June 1, 2024. The PuG is jointly organized with the Fachgruppe Biologische Psychologie und Neuropsychologie (FGBPNP) der Deutschen Gesellschaft für Psychologie  (DGPs) und der Deutschen Gesellschaft für Psychophysiologie und ihre Anwendung (DGPA).
 
We are positively surprised (one might even say overwhelmed) by the huge interest in this year’s PuG conference, and proudly present a program that features a rich set of scientific and networking events, including pre-conference workshops (organized by the Early Career Researchers), 35 scientific symposia with about 150 talks, two poster sessions with over 400 posters, poster flash talks, a Buddy program as well as general assemblies of the organizing societies (DGPs, DGPA) and the Special Interest Group of Open and Reproducible Research (IGOR). Opening and social evenings at the Universität Hamburg and on the historic cargo ship Cap San Diego round off the program. The three keynote lectures given by Karin Roelofs, Katharina von Kriegstein, and Nils Kroemer will certainly be highlights of the conference.
 
We are thrilled to gather an international community of researchers to explore developments and foster collaborations in biological psychology, neuropsychology and adjacent fields. We especially look forward to facilitating meaningful dialogues and collaborations among researchers at all stages of their careers. Hosting this year's conference in Hamburg offers a unique setting known for its dynamic intersection of tradition and innovation. As a city that has long been a gateway to the world, Hamburg mirrors the spirit of discovery and connectivity that we aim to promote in our scientific discussions.
 
Looking forward to welcoming you to Hamburg for an inspiring assembly of minds and ideas!
 
Best regards, the local organizing team of PuG 2024:

Helen Blank, Patrick Bruns, Sebastian Gluth, Tina Lonsdorf, Anja Riesel, Brigitte Röder, Nico Schuck, Lars Schwabe, Jan Wacker

\newpage