
            \begin{symposium}
            {S29 - Neural correlates of conscious experience: progress and challenges}
            {Torge Dellert}
            {Freitag 14:30 - 16:00 | Room 1.12/1.}
            {University of Münster}
            How does our brain generate consciousness, that is, our subjective experience of what it is like to see or feel? Recent years have seen remarkable progress in the search for its neural correlates. However, central aspects of their spatiotemporal dynamics are still hotly debated. The aim of this symposium is to showcase how rigorous behavioral and neuroscientific experiments can critically test competing theoretical predictions in the neuroscience of consciousness. While each talk will address a specific debate, a common focus will be on dissociating neural correlates of conscious experience from those of post-perceptual processes.
Torge Dellert (University of Münster) will highlight the importance of isolating neural correlates of consciousness from those of decision-making and show that they are graded rather than dichotomous. Darinka Trübutschek (MPIEA Frankfurt) will then challenge widely held assumptions about the role of memory for conscious perception based on behavioral, eye-tracking and MEG data. The next two talks will address previously neglected sustained rather than transient visual experiences. Antje Peters (University of Münster) will present EEG and fMRI studies, while Alex Lepauvre (MPIEA Frankfurt) will showcase intracranial and behavioral data from the Cogitate consortium and psychophysical experiments. Finally, Jona Förster (FU Berlin) will highlight neural correlates of conscious experiences in a previously understudied sensory modality: somatosensation.
Together, these presentations will demonstrate how carefully designed experiments can shed light on the neural basis of an inherently subjective phenomenon. We will finish the symposium with an open discussion of advances, challenges and future directions in the neuroscience of consciousness.
            \begin{description}    
            
                \item [ Dellert T.] Electrophysiological correlates of gradual awareness in the absence of decision-making \textcolor{mygray}{ | 14:30}    
                
                \item [ Trübutschek D.] Challenging current theories of conscious perception? - The case of activity-silent, non-conscious ‘working’ memory \textcolor{mygray}{ | 14:45}    
                
                \item [ Peters A.] Neural correlates of sustained conscious visual perception \textcolor{mygray}{ | 15:00}    
                
                \item [ Lepauvre A.] Temporal dynamics of visual conscious experience \textcolor{mygray}{ | 15:15}    
                
                \item [ Förster J.] EEG correlates of conscious somatosensory perception in a tactile temporal discrimination task \textcolor{mygray}{ | 15:30}    
                
            \end{description} 
            \end{symposium}
            