
            \begin{symposium}
            {S30 - Cognitive Schemas and Memory Generalization}
            {Session chair(s): Mona Garvert, Monika Schönauer}
            {Freitag 16:15 - 17:45 | Ort TODO}
            {Welche Uni TODO}
            Autoren: Mona Garvert, Monika Schönauer

To navigate a complex world successfully, we need to gather knowledge about the rules that govern it. By abstracting general knowledge from the experiences we make, we form flexible schemas that allow us to predict future outcomes and react appropriately. Drawing on multimodal brain imaging data and behavioral evidence, this symposium presents new evidence on how schemas guide human behavior and allow us to generalize to new experiences. The first two talks will focus on how cognitive schemas shape behavioral choices: Katja Kleespies will show that prior knowledge influences what we remember from everyday-like experiences, like visiting a supermarket or going to a restaurant, and that schema-related brain activity guides memory encoding and retrieval. Charley Wu will then demonstrate that we use complex compositional strategies to navigate such contexts, drawing on fragments of existing schemas to solve novel tasks, even under time pressure. The following speakers will shed light on how regularities are inferred from new experiences: Nico Schuck will show that both the hippocampus and the orbitofrontal cortex are involved in generalizing event structures across different environments. Felix Deilmann will present evidence that the hippocampus and prefrontal cortex represent distinct types of relational information, predictive contingencies between objects and the associated reward structure, and how we can generalize contingencies between these dimensions. Finally, Philipp Paulus will talk about how sleep aids the abstraction of rule-based contingencies in a category learning task, demonstrating that our brains continue to process information even after exploration has ended.
            \begin{description}    
            
                \item [Katja Kleespies (TODO: refactor name)] TODO: add title \textcolor{mygray}{ | 16:15}    
                
                \item [Charley M Wu (TODO: refactor name)] TODO: add title \textcolor{mygray}{ | 16:30}    
                
                \item [Nicolas Schuck  (TODO: refactor name)] TODO: add title \textcolor{mygray}{ | 16:45}    
                
                \item [Felix Deilmann  (TODO: refactor name)] TODO: add title \textcolor{mygray}{ | 17:00}    
                
                \item [Philipp Paulus (TODO: refactor name)] TODO: add title \textcolor{mygray}{ | 17:15}    
                
            \end{description} 
            \end{symposium}
            