
            \begin{symposium}
            {S25 - Mnemonic processing of immersive environments: Neuronal findings on different memory systems from virtual reality studies }
            { Joanna Kisker }
            {Freitag  - 12:30 | Ort TODO}
            {University of Stuttgart, Institute of Human Factors and Technology Management IAT, Applied Neurocognitive Systems}
            The majority of everyday memories is based on sensory-rich, three-dimensional experiences. For that reason, Virtual Reality (VR) is increasingly used to approximate realistic experiences. Yet little is known about how the neuronal correlates of memory derived from 2D-conditions translate to immersive conditions. Consequently, the symposium explores how different memory systems operate under VR-conditions, demonstrating both fundamental principles and practical applications. 
Anna Vorreuther presents a series of VR-fNIRS-studies examining the neuronal correlates of working memory load and associated learning progress. She demonstrates how brain-computer-interfaces can be utilized to develop and tailor immersive learning systems to individual needs and abilities. 
As Felix Klotzsche demonstrates, visual short-term memory is affected by the spatial relationship between stimulus and observer. By assessing the spatial constraints underlying two well-established electrophysiological markers of memory retention, he examines the effects of stimulus eccentricity. 
Likewise, spatial memory is facilitated by offering real-time 3D-content: Julia Belger presents an immersive Virtual Memory Task which allows for assessing, training and rehabilitating spatial memory deficits in neurologic patients, demonstrating the advantages of using VR in neuropsychological practice.
To unravel the dependence of episodic memory retrieval on the encoding modality, Joanna Kisker compares the electrophysiological correlates of retrieval of VR-based and 2D-based engrams, and demonstrates the potential to refine these findings by examining the high-frequency domain.
Concluding, Marike Johnsdorf presents a comprehensive investigation on how different degrees of reality affect object perception and mnemonic processing. Remarkably, she contrasts the neuronal correlates of a conventional laboratory, a realistic VR, and a real-life condition.
            \begin{description}    
            
                \item [ Vorreuther A.] fNIRS-Based Decoding of Mental State in Virtual Reality \textcolor{mygray}{ | 11:00}    
                
                \item [ Klotzsche F.] Title: The influence of stimulus eccentricity on short-term memory-related EEG components in virtual reality setups \textcolor{mygray}{ | 11:15}    
                
                \item [ Belger J.] Neuropsychological Application of Immersive Virtual Reality for Enhanced Spatial Memory Assessment and Rehabilitation \textcolor{mygray}{ | 11:30}    
                
                \item [ Kisker J.] How immersive features affect memory: Contrasting the retrieval of Virtual Reality-based and PC-based engrams on the electrophysiological level. \textcolor{mygray}{ | 11:45}    
                
                \item [ Johnsdorf M.] Object Perception and Memory Processing in Laboratory, Realistic Virtual, and Real-Life Environments: A Comparative EEG Analysis \textcolor{mygray}{ | 12:00}    
                
            \end{description} 
            \end{symposium}
            