
            \begin{symposium}
            {S19 - The versatile role of the endocannabinoid system in clinical research}
            {Daniela M. Pfabigan, Sara L. Kroll}
            {Freitag 09:00 - 10:30 | Room 1.18}
            {University of Bergen; University of Zurich}
            Recent years have seen an emergent interest in research of the endocannabinoid system (ECS). Endocannabinoid signalling plays a significant role in promoting stress buffering and reward-related behaviour. However, how endocannabinoids contribute to the presentation of clinical conditions, or how this system may be leveraged for novel therapeutics, is poorly understood. Therefore, this panel will highlight clinical research on the novel role of the ECS in psychiatric and non-psychiatric disorders.
This symposium will provide an overview of ongoing research that takes advantage of improved assessment methods and underlying knowledge concerning the ECS. Sara L. Kroll (University of Zurich) will start with an introduction to the ECS. Daniela M. Pfabigan (University of Bergen) will present a clinical trial design investigating changes in social experiences in individuals undergoing weight-loss surgery. This trial will link social experiences and well-being to hair concentrations of endocannabinoids as biological marker of well-being. Sara L. Kroll will show findings of an altered ECS in individuals with non-medical prescription opioid use (NMPOU) and discuss drug-related differences of peripheral endocannabinoids. Vinzenz K. Schmid (University of Zurich) will present recent findings of an altered endocannabinoid response to the psychosocial stressor of social exclusion within the same NMPOU population compared to controls. The symposium will be concluded by Marc D. Ferger (University of Cologne) talking about how non-suicidal self-injurious behaviours and childhood-tRooma are reflected in endocannabinoid concentrations in a large female adolescent sample. He will discuss the potential of using the ECS as a novel therapeutic target for psychiatric disorders
            \begin{description}    
            
                \item [ Pfabigan D.] Does bariatric surgery have a positive effect on patients’ social experiences and is this associated with the endocannabinoid system? – Study design of the BaSES study \textcolor{mygray}{ | 09:00}    
                
                \item [ Kroll S.] Peripheral endocannabinoids and their link to social stress in individuals with chronic non-medical prescription opioid use \textcolor{mygray}{ | 09:20}    
                
                \item [ Schmid V.] The Role of the Endocannabinoid System in Social Stress Reactivity among Non-medical Prescription Opioid Users: A Cyberball Paradigm Study  \textcolor{mygray}{ | 09:40}    
                
                \item [ Ferger M.] The endocannabinoid system in adolescents with non-suicidal self-injurious behavior and childhood trauma- new findings and promising therapeutic targets \textcolor{mygray}{ | 10:00}    
                
            \end{description} 
            \end{symposium}
            